Study locations

### 2022-11-08 Scripts/Map_study_locations.Rmd
file organization and renaming order
shiny app metadata

---
title: "Study locations"
output: html_document
---

@@

colors <- c("#8AD69E", "#74C5CE",  "#FDE9DE", "#45A631", "#95F7F0", "#CB53E1",
            "#FE90BB", "#B187E1", "#F8A982", "#0075DC", 
            "#993F00",  "#5EF1F2", "#005C31", "#74C5CE", "black", "lightblue",  "darkorange3","#8F7C00",
            "#8F7C00","#8F7C00", "#9DCC00", "#C20088", "gold1","#FFA8BB","#426600","94FFB5","#003380",  
            "#FF0010","#FF0010", "salmon", "seashell3","greenyellow","mediumaquamarine")
#To generate more random colors 
#randomcoloR::distinctColorPalette(k = length(file_names), altCol = F, runTsne = T)

>>>>

---
title: "Study locations"
output:
  html_document: default
  pdf_document: default
---

@@

colors <- c("#8AD69E", "#74C5CE",  "#FDE9DE", "#45A631", "#95F7F0", "#CB53E1",
            "#FE90BB", "#B187E1", "#F8A982", "#0075DC", 
            "#993F00",  "#5EF1F2", "#005C31", "#74C5CE", "black", "lightblue",  "darkorange3","#8F7C00",
            "#8F7C00","#8F7C00", "#9DCC00", "#C20088", "gold1","#FFA8BB","#426600","#94FFB5","#003380",  
            "#FF0010","#FF0010", "salmon", "seashell3","greenyellow","mediumaquamarine")
#To generate more random colors 
#randomcoloR::distinctColorPalette(k = length(file_names), altCol = F, runTsne = T)
